A Data-Driven Framework for Neural Field Modeling

### 2011-01-01 ltx/first_order_framework/LaTeX_Manuscript.tex
comment on  sampling
commit for pull

\subsection{Real time implementation}
\dean{(comment 1 and 9 from reviewer 2:) The implementation of the framework has been described a being appropriate for an evoked-potential experimental protocol. Over the time duration of an experimental paradigm the connectivity and synaptic kernel parameters are assumed to be stationary. However, if the method is applied to a continuous recording over a longer time duration it is unlikely that the parameters will be stationary. If fact, it is likely that changes in the parameter values would be of most interest. 
To implement the algorithm in a real-time scenario the we would assume that the parameters are stationary over a time period (window) where the estimation is performed. The parameter of the previous window can be used to initialize parameters of the next window.  }

>>>>

\subsection{Real time implementation}
\dean{(comment 1 and 9 from reviewer 2:) The implementation of the framework has been described a being appropriate for an evoked-potential experimental protocol. Over the time duration of an experimental paradigm the connectivity and synaptic kernel parameters are assumed to be stationary. However, if the method is applied to a continuous recording over a longer time duration it is unlikely that the parameters will be stationary. If fact, it is likely that changes in the parameter values would be of most interest.}

\dean{To implement the algorithm in a real-time scenario the we would assume that the parameters are stationary over a time period (window) where the estimation is performed. The parameter of the previous window can be used to initialize parameters of the next window.}
